Results exploration

### 2023-03-17 README.Rmd
manuscript.Rmd runs the preprocessing files in a new R session safely, readme updated with instructions on how to run interactive document and replicate the restuls

@@

The `manuscript/` folder contains the manuscript and supplementary materials documents with the analysis code embedded in them.

>>>>

__In order to replicate our results including the whole data preprocessing procedure with one click, please knit the `manuscript/manuscript.Rmd` file.__

@@

The `manuscript/` folder contains the manuscript and supplementary materials documents with the analysis code embedded in them. The folder also includes the `interactive_report.Rmd` file, which includes an interactive document for reanalysing our results with different subsets of the data. To run the interactive document locally on your computer, click the _Run document_ button in Rstudio or run the `rmarkdown::run(here::here("manuscript/interactive_report.Rmd"))` function in your R console.

### 2023-03-17 manuscript/manuscript.Rmd
manuscript.Rmd runs the preprocessing files in a new R session safely, readme updated with instructions on how to run interactive document and replicate the restuls

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
library("papaja")
library(tidyverse)
library(here)
library(kableExtra)
library(gt)
library(patchwork)
# The developer version is needed
library(likert)
library(viridis)
# r_refs("references.bib")
```

@@

```{r preprocessing}
# loads source data, performs preprocessing, saves raw datafiles
# source(here("preprocessing", "ecaw_source_raw_preprocessing.R"))

# loads raw data, performs preprocessing, saves processed datafiles
# source(here("preprocessing", "ecaw_raw_processed_preprocessing.R"))
```

```{r loading_data}
processed <- read_csv(here("data/processed/ecaw_processed_data.csv"))
```

>>>>

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
library("papaja")
library(tidyverse)
library(here)
library(kableExtra)
library(gt)
library(patchwork)
# The developer version is needed
library(likert)
library(knitr)
library(viridis)
# r_refs("references.bib")
```

@@

```{r preprocessing, include=FALSE}
# loads source data, performs preprocessing, saves raw datafiles
xfun::Rscript_call(
  rmarkdown::render,
  list(
    input = here::here("preprocessing", "ecaw_source_raw_preprocessing.Rmd"),
    output_format = 'html_document')
  )

# loads raw data, performs preprocessing, saves processed datafiles
xfun::Rscript_call(
  rmarkdown::render,
  list(
    input = here::here("preprocessing", "ecaw_raw_processed_preprocessing.Rmd"),
    output_format = 'html_document')
  )
```

```{r loading_data}
processed <- read_csv(here::here("data/processed/ecaw_processed_data.csv"))
```

### 2023-03-17 manuscript/supplementary_materials_c.Rmd
manuscript.Rmd runs the preprocessing files in a new R session safely, readme updated with instructions on how to run interactive document and replicate the restuls

# Create likert package data not including the missing values
concerned_plot_data <- likert(filter(concerned_plot_data, !is.na(concerned)))

# Create figure
plot(concerned_plot_data, digits = 1, text.size = 6) +
  labs(title = "Compared to what you think of as a typical researcher who uses preexisting observational data in your field,\nhow concerned are you with research trustworthiness, bias, rigour, and reproducibility ...") +
  theme(
    title = element_text(size = 14),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 15),
    axis.title.x = element_text(size = 15),
    legend.text = element_text(size = 10),
    legend.title = element_blank()
  )
```

>>>>

concerned_plot_data <- filter(concerned_plot_data, !is.na(concerned))

# Create likert package data not including the missing values
concerned_likert_plot_data <- likert(concerned_plot_data)

# Create figure
plot(concerned_likert_plot_data, digits = 1, text.size = 6, group.order = names(concerned_plot_data)) +
  labs(title = "Compared to what you think of as a typical researcher who uses preexisting observational data in your field,\nhow concerned are you with research trustworthiness, bias, rigour, and reproducibility ...") +
  theme(
    title = element_text(size = 14),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 15),
    axis.title.x = element_text(size = 15),
    legend.text = element_text(size = 10),
    legend.title = element_blank()
  )
```
